Firstly, of course, I would like to thank Gareth Alexander, who has been a frankly unreasonably good supervisor over the past four years --- I feel a little spoilt. Thank you for always having your door open and patiently teaching me the rudiments of algebraic topology, differential geometry, characteristic classes and more abstract mathematics generally --- there is an alternate reality where I never learn any of these things. Thank you also for constantly coming up with a stream of good ideas, and your support and (incredibly close!) proofreading as I learnt to write papers. I really could not have done this without you. The work in the third chapter of this thesis was started while Carl Whitfield was at Warwick, and in the fourth was done jointly with Joe Pollard --- thank you both for being a pleasure to work with. Thank you also to Ray Goldstein and the David Crighton Memorial fund for funding and hosting me during a three month stint in Cambridge.  

The Centre for Complexity Science and the MathSys CDT has been such a welcoming environment over the past four years, and I wish to thank everyone involved in its organisation for making it so --- it is not the norm for PhD students to instantly feel they have a community, and I cannot overemphasise how much of a difference this makes in terms of ones daily emotional life. Thank you in particular to Heather Robson and Debbie Walker, the wonderful group secretaries, for making everything work.  My cohort, and those in the years above and below me, have been uniformly lovely. Thank you to all my friends and office mates over the years for putting up with my various neuroses --- in particular Gian, Giovanni, Katherine, Sami, Jon my work and climbing wife, and the incomparably amazing Jim and Iliana. Thank you also to S, J, K, O, N, L, O, E, H and M for letting me vent.

Thank you to my parents, Julie and Howard, my sisters Sarah and Elana, and my dog Tess who I assume is immortal, for all your love and support --- sorry I have been a little out of touch. Yes Mum, I've finished my PhD now. No Mum, I don't know what I'm going to do next. Thank you also to my Grandfather Harry, for enabling further education within our family --- I'm sorry you didn't get to see me finish this.

 Lastly, thank you Becky --- my favourite Knot(t) of all.

